Machine learning enhanced empirical potentials for metals and alloys

### 2020-06-03 doc/papers/ml-eam/manuscript.tex
Minor update for cpc.

For the first step, the implementation is almost the same with our previous 
work \cite{TensorAlloy} except the formula of the potential energy. Briefly, 
this step starts from checking through the training dataset and determine some
key constants, including $N^{vap}$ and $N^{\mathrm{max}}_{\mathrm{ij}}$. 
$N^{\mathrm{max}}_{\mathrm{ijk}}$ is not needed as neither EAM nor ADP contains 
triple-atoms interaction. Then we can build the global symbol list (GSL). Hence,
structures of any stoichiometries can be transformed to their corresponding 
unversal GSL forms for batching. The descriptors (\ref{sec:transformation}) are 
built upon these GSL arrays. Then the direct computation graph from atomic 
positions (GSL) to total energy can be easily built. Hence, atomic forces and 
virial stress tensors can be calculated automatically thanks to the AutoGrad 
feature of TensorFlow.

>>>>

For the first step, the implementation is almost the same with our previous 
work \cite{TensorAlloy} except the formula of the potential energy. Briefly, 
this step starts from checking through the training dataset and determine some
key constants, including the global symbol list and its size $N^{vap}$. For 
arbitrary structure, it has $N_{ij}$ different atom-atom pairs within cutoff 
$r_c$. For a concrete dataset, the corresponding maximum 
$N^{\mathrm{max}}_{\mathrm{ij}}$ can also be determined before training. Hence,
Structures of any stoichiometries can be transformed to their corresponding 
universal GSL forms for batching. The descriptors (\ref{sec:transformation}) are 
built upon these GSL arrays. Then the direct computation graph from atomic 
positions (GSL) to total energy can be easily built. Hence, atomic forces and 
virial stress tensors can be calculated automatically thanks to the AutoGrad 
feature of TensorFlow.
